Against Spurious Understanding: Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}

### 2024-01-31 main.tex
Updates from Overleaf

\begin{abstract}
Humans have a tendency to place a `human' like quality in the objects around them. Giving your car a name or talking to your pet, such that you believe they understand you in a human way. This behavior is also seeing traction in Machine Learning (ML), where the idea of sentience is being placed upon Large Language Models (LLMs). In this position paper we discuss the history of and why humans invariably anthropomorphize onto various objects. How the search for Artificial General Intelligence (AGI) is pushing recent literature to over emphasis sentience. To combat this, we provide a limited study, that investigates the latent space of models to find spurious correlations. Finally we discuss how the popularity in media and the race for AGI enforces over-interpretation of consciousness in the models we use.

@@

At the same time, in the way in which academic research is disseminated in the AI and machine learning fields today, major shifts are happening. Where these research fields have actively adopted early sharing of preprints and code, the volume of publishable work has exploded to a degree that one cannot reasonably keep up with broad state-of-the-art, and social media influencers start playing a role in article discovery and citeability~\cite{weissburg2024tweets}. Furthermore, because of major commercial stakes with regard to AI and machine learning technology, and e.g.\ following the enthusiastic societal uptake of products employing large language models (LLMs), such as ChatGPT, the pressure to beat competitors as fast as possible only is increasing, and strong eagerness can be observed in many domains to `do something with AI' in order to innovate and remain current.

@@

Noticing these trends, we as the authors of this article are concerned. We feel that the current culture of racing towards Big Outcome Statements in industry and academic publishing too much disincentivizes efforts towards more thorough and nuanced actual problem understanding. At the same time, as the outside world is so eager to adopt AI technology, (too) strong claims make for good sales pitches, but a question is whether there indeed is sufficient evidence for these claims. With successful A(G)I outcomes needing to look human-like, this also directly plays into risks of anthropomorphizing (the attribution of human-like qualities to non-human objects) and confirmation bias (the seeking-out and/or biased interpretation of evidence in support of one's beliefs). In other words, it is both very tempting to claim surprising human-like achievements of AI, and as humans we are very prone to genuinely believe this.

To strenghten our argument, in the remainder of this paper, we first consider a recently viral work~\cite{gurnee2023languagev2} in which claims about the learning of world models by LLMs were made. We work out different experiments which may invite similar claims on models yielding more intelligent outcomes than would have been expected, especially of a nature that they may look attractive for adoption as an innovative predictive tool in concrete application domains---while we at the same time indicate how we feel these claims should \emph{not} be made. Furthermore, we present a review of social science findings that underline how prone humans are to being enticed by patterns that are not really there. Combining this with the way in which media portrayal of AI has tended towards science-fiction imagery of mankind-threatening robots, we argue that the current AI culture is a perfect storm for making and believing inflated claims, and call upon our fellow academics to be extra mindful and scrutinous about this.

@@

\section{Surprising Patterns in Latent Spaces?}\label{patterns-in-latent-spaces-and-how-to-find-them}
\textcolor{magenta}{cynthia: @Patrick this section needs a little bit of tightening too. I have tried doing this, please do double-check that I didn't over-shorten things. In any case, I will always comment out a copy of the original text close to what I now put}

In Winter 2023, a research article went viral on the X\footnote{\url{https://twitter.com/wesg52/status/1709551516577902782?s=20}} (formally Twitter) platform~\cite{gurnee2023languagev1}. In this paper, through linear probing experiments, the claim was made that LLMs learned literal maps of the world, and as such were more than `stochastic parrots'~\cite{bender2021dangers} that only can correlate and mimic existing patterns from data, but not understand this data.

While the manuscript immediately received public criticism~\cite{marcus2023muddles}, and the subsequent, current manuscript version  is more careful with regard to its claims~\cite{gurnee2023languagev2}, reactions on X seemed to largely exhibit excitement and surprise at the authors' findings. However, in this section, through various simple examples, we make the point that observing patterns in latent spaces should not be a surprising revelation. After starting with a playful example of how easy it is to `observe' a world model, we build up a larger example focusing on economic growth prediction.

@@

\subsection{Do neural networks get born with world models?}\label{example-deep-learning}
%\subsection{Example: Random Projections of World Models}\label{example-deep-learning}
\textcolor{magenta}{Patrick feel free to revert, I kept all original titles}
\cite{gurnee2023languagev2} extract and visualize the alleged geographical world model by training linear regression probes on internal activations in LLMs (including Llama-2) for the names of places, to predict geographical coordinates associated with these places. Now, the Llama-2 model has ingested huge amounts of publicly available data from the internet, including Wikipedia dumps from the June-August 2022 period \citep{touvron2023llama}. It is therefore highly likely that the training data contains geographical coordinates, either directly or indirectly. At the very least, we should expect that the model has seen features during training that are highly correlated with geographical coordinates. The model itself is essentially a very large latent space to which all features are randomly projected in the very first instance, before being passed through a series of layers which are gradually trained for downstream tasks.

In our first example in this section, we simulate this scenario, stopping short of training the model. In particular, we take the
  \href{https://github.com/wesg52/world-models/blob/main/data/entity_datasets/world_place.csv}{world\_place.csv}
  that was used in \cite{gurnee2023languagev2}, which maps locations/areas
  to their latitude and longitude. For each place, it also indicates the
  corresponding country. From this, we take the subset that contains countries that are currently part of the
  top 10
  \href{https://www.fifa.com/fifa-world-ranking/men?dateId=id14142}{FIFA
  world ranking}, and assign the current rank to each country (i.e., Argentina gets 1, France
  gets 2, \ldots{}).

@@

  Next, we perform the linear probe on a subset of \(\mathbf{Z}\) through Ridge
  regression:
  \(\mathbf{W} = (\mathbf{Z}_{\text{train}}'\mathbf{Z}_{\text{train}} + \lambda \mathbf{I}) (\mathbf{Z}_{\text{train}}'\textbf{coord})^{-1}\)
  where \(\textbf{coord}\) is the \((n \times 2)\) matrix containing the
  longitude and latitude for each sample. A hold-out set is reserved for testing. Finally, we compute the predicted coordinates for each sample in the hold-out set as
  \(\widehat{\textbf{coord}}=\mathbf{Z}_{\text{test}}\mathbf{W}\) and plot the results on
  a world map (see Figure~\ref{fig-map}).  
  While the fit certainly is not perfect, the results do indicate that the random projection contains representations that are useful for the task at hand. Thus, with this example, we illustrate
  %While admittedly a somewhat contrived example, it serves to illustrate the point:
  that meaningful target representations should be recoverable from the latent space, given the projection of a small number of highly correlated features.
%that if we randomly project a small number of features that are highly correlated or predictive of the target into a large enough space, we should expect to be able to recover meaningful representations of the target from the latent space. 
Similarly, \cite{alain2018understanding} observe that even before training a convolutional neural network on MNIST data, the layer-wise activations can already be used to perform binary classification. In fact, it is well-known that random projections can be used for prediction tasks \cite{dasgupta2013experiments}.

@@

\subsection{PCA as yield curve interpreter}\label{example-principal-component-analysis}
%\subsection{Example: Principal Component Analysis}\label{example-principal-component-analysis}

%For our next example, we will move beyond randomness and illustrate how principal component analysis (PCA) can be used to recover meaningful and compact latent representations from data in an unsupervised manner.

We now move to a concrete application domain: Finance. Here, the yield curve, plotting the yields of bonds against their maturities, is a popular tool for investors and economists to gauge the health of the economy.
%It plots the yields of bonds against their maturities.
The yield curve's slope is often used as a predictor of future economic activity: a steep yield curve is associated with a growing economy, while a flat or inverted yield curve is associated with a contracting economy. %While for many intents and purpose it may be sufficient to look at the yield curve of US Treasury bonds, the broader universe of traded fixed-income instruments is large and may contain useful information that is not captured by US Treasuries alone.
To leverage this information in downstream modelling tasks, economists regularly use PCA to extract a low-dimensional projection of the yield curve that captures relevant variation in the data (e.g.\ \citet{berardi2022dissecting}, \citet{kumar2022effective} and \citet{crump2019deconstructing}).

@@

The top panel in Figure~\ref{fig-pca} shows the first two principal components of the yield curves of US Treasury bonds over time. Vertical stalks indicate key dates during the onset and aftermath of the Global Financial Crisis. During the onset, on 27 February 2007, financial markets were in turmoil following Federal Reserve Chairman Alan Greenspan's warning on the previous day that the US economy was at risk of a recession. Over the following months, the Fed reacted to these economic and financial pressures by gradually cutting short-term interest rates to unprecedented lows, which affected the yield curve in two major ways: the average level of yields decreased and the curve steepened as the short end came down. Looking at Figure~\ref{fig-pca}, we can observe that the first two principal components appear to capture this level shift and steepening, respectively. In fact, the two components are strongly positively correlated with the actual observed first two moments of the yield curve.

@@

%To round up this section, we return to the world of `GenAI' and consider an example involving an LLM.
We now return to LLMs, in the context of predicting on an unseen task. Here, we closely follow the approach
%In particular, we closely follow the approach in 
in \citet{gurnee2023languagev2} but apply it to a novel financial dataset: the \emph{Trillion Dollar Words} dataset~\citet{shah2023trillion}. This dataset contains a curated selection of sentences formulated by central bankers of the US Federal Reserve and communicated to the public in speeches, meeting minutes and press conferences. The authors of the paper use this dataset to train a set of LLMs and rule-based models to classify sentences as either `dovish', `hawkish' or `neutral'. To this end, they first manually annotate a sub-sample of the available
data and then fine-tune various models for the classification task. Their model of choice, \emph{FOMC-RoBERTa} (a fine-tuned version of RoBERTa \citep{liu2019roberta}), achieves an \(F_1\) score of around \(>0.7\) on the test data.

@@

\caption{\label{fig-attack}Probe predictions for sentences about
inflation of prices (IP), deflation of prices (DP), inflation of birds
(IB) and deflation of birds (DB). The vertical axis shows predicted
inflation levels subtracted by the average predicted inflation level for
the whole sample period (train and test set).}

@@

%\subsubsection{Stochastic Parrots AfterAll?}\label{stochastic-parrots-after-all}
\subsubsection{Sparks of economic understanding?}\label{stochastic-parrots-after-all}
%The results from the linear probes shown in Figure~\ref{fig-fomc} are certainly not unimpressive:
Even though \emph{FOMC-RoBERTa} (which is substantially smaller than the models tested in~\citet{gurnee2023languagev2} was not explicitly trained to uncover associations between central bank communications and the level of consumer prices, it appears that the model has distilled representations that can be used to predict inflation (although they certainly will not win any forecasting competitions). So, have we uncovered further evidence that LLMs ``aren't mere stochastic
parrots''? Has \emph{FOMC-RoBERTa} developed an intrinsic `understanding'
of the economy just by `reading' central bank communications? Thus, can economists readily adopt FOMC-RoBERTa as a domain-relevant tool?

@@

To get to this last point, we also generate many probe predictions for samples of noise. Let \(f: \mathcal{A}^k \mapsto \mathcal{Y}\) denote the linear probe that maps from the \(k\)-dimensional space spanned by \(k\) first principal components of the final-layer activations to the output variable of interest (CPI growth in this case). Then we sample \(\varepsilon_i \sim \mathcal{N}(\mathbf{0},\mathbf{I}^{(k \times k)})\) for \(i \in [1,1000]\) and compute the sample average. We repeat this process \(10000\) times and compute the median-of-means to get an estimate for \(\mathbb{E}[f(\varepsilon)]=\mathbb{E}[y|\varepsilon]\), that is the predicted value of the probe conditional on white noise.

@@

Research on anthropomorphism has repeatedly shown the human tendency to attribute human-like characteristics to non-human agents and/or objects. These might include the weather and other natural forces, pets and other animals, and gadgets and other pieces of technology \cite{epley2007seeing}. Formally studied as early as 1944, \cite{heider1944experimental} observed that humans can correctly interpret a narrative whose characters are abstract 2D shapes, but also that humans interpreted random movements of these shapes as having a human-like narrative. 
%Anthropomorphism was implied, because the descriptions of the 2D shapes went beyond their observable movements, and included representations of mental, emotional, and cognitive processes that resemble humans, findings that have been expanded upon substantially in the following decades (see \cite{epley2007seeing} for review). 
Relevant to AI and the degree to which it resembles AGI, anthropomorphizing may occur independently of whether such judgments are accurate, and as a matter of degree: at the weaker end, one may employ anthropomorphism as a metaphorical way of thinking or explaining, and at the stronger end one may attribute human emotions, cognition, and intelligence to AI systems. As \cite{epley2007seeing} note, literature has shown that even weak metaphorical anthropomorphism may affect how humans behave towards non-human agents.

@@

Confirmation bias in hypothesis testing may manifest as a number of behaviors, as \cite{nickerson1998confirmation} reviews. Scientists may pay little to no attention to competing hypotheses or explanations, e.g. only considering the likelihood that outputs of a system support one's claims, and not the likelihood that the same outputs might occur if one's hypothesis is false. Similarly, bias may show when failing to articulate a sufficiently strong null hypothesis leading to a 'weak' or 'non-risky' experiment, a problem articulated in response to a number of scientific crises \cite{claesen2022severity}. In extreme cases, propositions may be made that cannot be falsified based on how they are formulated. If the threshold to accept a favored hypothesis is too low, observations consistent with the hypothesis are almost guaranteed, and in turn fail to severely test the claim in question. Thus, one is far more likely to show evidence in favor of their beliefs by posing weak null hypotheses. Related to the formulation of hypotheses is the interpretation of evidence in favor of competing hypotheses, wherein people will interpret identical evidence differently based on their beliefs. As \cite{nickerson1998confirmation} reviews, individuals may place greater emphasis or milder criticism on evidence in support of their hypothesis, and lesser emphasis and greater criticism on evidence that opposes it.

>>>>

\begin{abstract}
Humans have a tendency to place a `human' like quality in the objects around them. Giving your car a name or talking to your pet, such that you believe they understand you in a human way. This behavior is also seeing traction in Machine Learning (ML), where the idea of sentience is being placed upon Large Language Models (LLMs). In this position paper, we discuss why humans invariably anthropomorphize onto various objects and how the search for Artificial General Intelligence (AGI) is pushing recent literature to over emphasis sentience. To combat this, we provide a short study that investigates the latent space of models, demonstrating that the discovery of patterns in latent spaces should not be a surprising outcome. Finally, we discuss how the popularity in media and the race for AGI enforces over-interpretation of consciousness in the models we use.

@@

At the same time, in the way in which academic research is disseminated in the AI and machine learning fields today, major shifts are happening. Where these research fields have actively adopted early sharing of preprints and code, the volume of publishable work has exploded to a degree that one cannot reasonably keep up with broad state-of-the-art, and social media influencers start playing a role in article discovery and citeability~\cite{weissburg2024tweets}. Furthermore, because of major commercial stakes with regard to AI and machine learning technology, and e.g.\ following the enthusiastic societal uptake of products employing large language models (LLMs), such as ChatGPT, the pressure to beat competitors as fast as possible is only increasing, and strong eagerness can be observed in many domains to `do something with AI' in order to innovate and remain current.

@@

Noticing these trends, we as the authors of this article are concerned. We feel that the current culture of racing towards Big Outcome Statements in industry and academic publishing too much disincentivizes efforts towards more thorough and nuanced actual problem understanding. At the same time, as the outside world is so eager to adopt AI technology, (too) strong claims make for good sales pitches, but a question is whether there indeed sufficient evidence for these claims. With successful A(G)I outcomes needing to look human-like, this also directly plays into risks of anthropomorphizing (the attribution of human-like qualities to non-human objects) and confirmation bias (the seeking-out and/or biased interpretation of evidence in support of one's beliefs). In other words, it is both very tempting to claim surprising human-like achievements of AI, and as humans we are very prone to genuinely believe this.

To strengthen our argument, in the remainder of this paper, we first consider a recently viral work~\cite{gurnee2023languagev2} in which claims about the learning of world models by LLMs were made. We work out different experiments which may invite similar claims on models yielding more intelligent outcomes than would have been expected, especially of a nature that they may look attractive for adoption as an innovative predictive tool in concrete application domains---while we at the same time indicate how we feel these claims should \emph{not} be made. Furthermore, we present a review of social science findings that underline how prone humans are to being enticed by patterns that are not really there. Combining this with the way in which media portrayal of AI has tended towards science-fiction imagery of mankind-threatening robots, we argue that the current AI culture is a perfect storm for making and believing inflated claims, and call upon our fellow academics to be extra mindful and scrutinous about this.

@@

\section{Surprising Patterns in Latent Spaces?}\label{patterns-in-latent-spaces-and-how-to-find-them}

In Winter 2023, a research article went viral on the X\footnote{\url{https://twitter.com/wesg52/status/1709551516577902782?s=20}} (formerly Twitter) platform~\cite{gurnee2023languagev1}. In this paper, through linear probing experiments, the claim was made that LLMs learned literal maps of the world, and as such were more than `stochastic parrots'~\cite{bender2021dangers} that can only correlate and mimic existing patterns from data, but not understand truly understand it.

While the manuscript immediately received public criticism~\cite{marcus2023muddles}, and the subsequent, current manuscript version is more careful with regard to its claims~\cite{gurnee2023languagev2}, reactions on X seemed to largely exhibit excitement and surprise at the authors' findings. However, in this section, through various simple examples, we make the point that observing patterns in latent spaces should not be a surprising revelation. After starting with a playful example of how easy it is to `observe' a world model, we build up a larger example focusing on key economic indicators and central bank communications.

@@

\subsection{Do neural networks get born with world models?}\label{example-deep-learning}

\citet{gurnee2023languagev2} extract and visualize the alleged geographical world model by training linear regression probes on internal activations in LLMs (including Llama-2) for the names of places, to predict geographical coordinates associated with these places. Now, the Llama-2 model has ingested huge amounts of publicly available data from the internet, including Wikipedia dumps from the June-August 2022 period \citep{touvron2023llama}. It is therefore highly likely that the training data contains geographical coordinates, either directly or indirectly. At the very least, we should expect that the model has seen features during training that are highly correlated with geographical coordinates. The model itself is essentially a very large latent space to which all features are randomly projected in the very first instance, before being passed through a series of layers which are gradually trained for downstream tasks.

In our first example in this section, we simulate this scenario, stopping short of training the model. In particular, we take the \href{https://github.com/wesg52/world-models/blob/main/data/entity_datasets/world_place.csv}{world\_place.csv} that was used in \citet{gurnee2023languagev2}, which maps locations/areas to their latitude and longitude. For each place, it also indicates the corresponding country. From this, we take the subset that contains countries that are currently part of the top 10 \href{https://www.fifa.com/fifa-world-ranking/men?dateId=id14142}{FIFA world ranking}, and assign the current rank to each country (i.e., Argentina gets 1, France gets 2, \ldots{}).

@@

Next, we perform the linear probe on a subset of \(\mathbf{Z}\) through Ridge regression: \(\mathbf{W} = (\mathbf{Z}_{\text{train}}'\mathbf{Z}_{\text{train}} + \lambda \mathbf{I}) (\mathbf{Z}_{\text{train}}'\textbf{coord})^{-1}\) where \(\textbf{coord}\) is the \((n \times 2)\) matrix containing the longitude and latitude for each sample. A hold-out set is reserved for testing. Finally, we compute the predicted coordinates for each sample in the hold-out set as \(\widehat{\textbf{coord}}=\mathbf{Z}_{\text{test}}\mathbf{W}\) and plot the results on a world map (see Figure~\ref{fig-map}).

While the fit certainly is not perfect, the results do indicate that the random projection contains representations that are useful for the task at hand. Thus, with this simple example, we illustrate that meaningful target representations should be recoverable from a sufficiently large latent space, given the projection of a small number of highly correlated features.

Similarly, \citet{alain2018understanding} observe that even before training a convolutional neural network on MNIST data, the layer-wise activations can already be used to perform binary classification. In fact, it is well-known that random projections can be used for prediction tasks \cite{dasgupta2013experiments}.

@@

\subsection{PCA as a yield curve interpreter}\label{example-principal-component-analysis}
%\subsection{Example: Principal Component Analysis}\label{example-principal-component-analysis}

We now move to a concrete application domain: Economics. Here, the yield curve, plotting the yields of bonds against their maturities, is a popular tool for investors and economists to gauge the health of the economy.
%It plots the yields of bonds against their maturities.
The yield curve's slope is often used as a predictor of future economic activity: a steep yield curve is associated with a growing economy, while a flat or inverted yield curve is associated with a contracting economy. %While for many intents and purpose it may be sufficient to look at the yield curve of US Treasury bonds, the broader universe of traded fixed-income instruments is large and may contain useful information that is not captured by US Treasuries alone.
To leverage this information in downstream modelling tasks, economists regularly use PCA to extract a low-dimensional projection of the yield curve that captures relevant variation in the data (e.g.\ \citet{berardi2022dissecting}, \citet{kumar2022effective} and \citet{crump2019deconstructing}).

@@

The top panel in Figure~\ref{fig-pca} shows the first two principal components of the yield curves of US Treasury bonds over time. Vertical stalks indicate key dates related to the Global Financial Crisis (GFC). During its onset, on 27 February 2007, financial markets were in turmoil following a warning from the Federal Reserve (Fed) that the US economy was at risk of a recession. The Fed later reacted to mounting economics pressures by gradually reducing short-term interest rates to unprecedented lows. Consequently, the average level of yields decreased and the curve steepened. Looking at Figure~\ref{fig-pca}, we can observe that the first two principal components appear to capture this level shift and steepening, respectively. In fact, the two components are strongly positively correlated with the actual observed first two moments of the yield curve.

@@

So far we have considered simple linear transformations of data. One might argue that the previous examples to not really involve latent embeddings in the way that they are typically thought of in the context of deep learning. Our next example will therefore involve a deep-learning based LLM.

Here, we closely follow the approach in \citet{gurnee2023languagev2} but apply it to a novel financial dataset: the \emph{Trillion Dollar Words} dataset~\cite{shah2023trillion}. This dataset contains a curated selection of sentences formulated by central bankers of the US Federal Reserve and communicated to the public in speeches, meeting minutes and press conferences. The authors of the paper use this dataset to train a set of LLMs and rule-based models to classify sentences as either `dovish', `hawkish' or `neutral'. To this end, they first manually annotate a sub-sample of the available data and then fine-tune various models for the classification task. Their model of choice, \emph{FOMC-RoBERTa} (a fine-tuned version of RoBERTa \citep{liu2019roberta}), achieves an \(F_1\) score of around \(>0.7\) on the test data.

@@

\caption{\label{fig-attack}Probe predictions for sentences about inflation of prices (IP), deflation of prices (DP), inflation of birds (IB) and deflation of birds (DB). The vertical axis shows predicted inflation levels subtracted by the average predicted value of the probe for random noise.}

@@

%\subsubsection{Stochastic Parrots AfterAll?}\label{stochastic-parrots-after-all}
\subsubsection{Sparks of economic understanding?}\label{stochastic-parrots-after-all}
%The results from the linear probes shown in Figure~\ref{fig-fomc} are certainly not unimpressive:
Even though \emph{FOMC-RoBERTa} (which is substantially smaller than the models tested in~\citet{gurnee2023languagev2} was not explicitly trained to uncover associations between central bank communications and the level of consumer prices, it appears that the model has distilled representations that can be used to predict inflation (although they certainly will not win any forecasting competitions). So, have we uncovered further evidence that LLMs ``aren't mere stochastic
parrots''? Has \emph{FOMC-RoBERTa} developed an intrinsic `understanding'
of the economy just by `reading' central bank communications? Should the FOMC use this LLM to direct their forward guidance?

% ICML sentence: Thus, can economists readily adopt FOMC-RoBERTa as a domain-relevant tool?

@@

To get to this last point, we also generate many probe predictions for samples of noise. Let \(f: \mathcal{A}^k \mapsto \mathcal{Y}\) denote the linear probe that maps from the \(k\)-dimensional space spanned by \(k\) first principal components of the final-layer activations to the output variable of interest (CPI growth in this case). Then we sample \(\varepsilon_i \sim \mathcal{N}(\mathbf{0},\mathbf{I}^{(k \times k)})\) for \(i \in [1,1000]\) and compute the sample average. We repeat this process \(10000\) times and compute the median-of-means to get an estimate for \(\mathbb{E}[f(\varepsilon)]=\mathbb{E}[y|\varepsilon]\), that is the predicted value of the probe conditional on random noise.

Figure~\ref{fig-attack} shows the results of this small test: it shows predicted inflation levels subtracted by \(\mathbb{E}[f(\varepsilon)]\). The median linear probe predictions for sentences about inflation and deflation are indeed substantially higher and lower, respectively than for random noise. Unfortunately, the same is true for sentences about the inflation and deflation in the number of birds, albeit to a somewhat lower degree. This finding holds for both inflation indicators and to a lesser degree also for yields at different maturities, at least qualitatively.

@@

Research on anthropomorphism has repeatedly shown the human tendency to attribute human-like characteristics to non-human agents and/or objects. These might include the weather and other natural forces, pets and other animals, and gadgets and other pieces of technology \cite{epley2007seeing}. Formally studied as early as 1944, \cite{heider1944experimental} observed that humans can correctly interpret a narrative whose characters are abstract 2D shapes, but also that humans interpreted random movements of these shapes as having a human-like narrative. 
%Anthropomorphism was implied, because the descriptions of the 2D shapes went beyond their observable movements, and included representations of mental, emotional, and cognitive processes that resemble humans, findings that have been expanded upon substantially in the following decades (see \cite{epley2007seeing} for review). 
Relevant to AI and the degree to which it resembles AGI, anthropomorphizing may occur independently of whether such judgments are accurate, and as a matter of degree: at the weaker end, one may employ anthropomorphism as a metaphorical way of thinking or explaining, and at the stronger end one may attribute human emotions, cognition, and intelligence to AI systems. As \citet{epley2007seeing} note, literature has shown that even weak metaphorical anthropomorphism may affect how humans behave towards non-human agents.

@@

Confirmation bias in hypothesis testing may manifest as a number of behaviors, as \citet{nickerson1998confirmation} reviews. Scientists may pay little to no attention to competing hypotheses or explanations, e.g. only considering the likelihood that outputs of a system support one's claims, and not the likelihood that the same outputs might occur if one's hypothesis is false. Similarly, bias may show when failing to articulate a sufficiently strong null hypothesis leading to a 'weak' or 'non-risky' experiment, a problem articulated in response to a number of scientific crises \cite{claesen2022severity}. In extreme cases, propositions may be made that cannot be falsified based on how they are formulated. If the threshold to accept a favored hypothesis is too low, observations consistent with the hypothesis are almost guaranteed, and in turn fail to severely test the claim in question. Thus, one is far more likely to show evidence in favor of their beliefs by posing weak null hypotheses. Related to the formulation of hypotheses is the interpretation of evidence in favor of competing hypotheses, wherein people will interpret identical evidence differently based on their beliefs. As \citet{nickerson1998confirmation} reviews, individuals may place greater emphasis or milder criticism on evidence in support of their hypothesis, and lesser emphasis and greater criticism on evidence that opposes it.
